---
output:
  pagedown::html_paged:
    css: ["css/one-column-paged-academic.css", "css/academicons.min.css",
          "css/css/all.css"]
#"https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: false
title: "Ethan Hurwitz CV"
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
library(glue)
library(googlesheets4)

######## rerun googlesheet syncing to make sure files are up to date!
source("sync_w_gsheets.R", local = knitr::knit_global())

######## CREATE HELPER FUNCTIONS
# function which takes a name and replaces the first name with initial and dot
replace_first_name_with_initial_and_dot <- function(author_name) {
  str_replace(author_name, "(?<=\\S)\\S+", "\\.")
}

# function for doing this for an entry with a number of authors
replace_first_names_in_list_with_initial_and_dot <- function(authors){
  authors_split <- str_split(authors, ",") %>% 
    map(str_trim)
  
  authors_split[[1]] %>% map_chr(replace_first_name_with_initial_and_dot) %>% 
    paste0(collapse = ", ")
}

# function for adding leading zero's when there's more than 10 entries
padding_function <- function(cv_entries_tibble, letter_to_pad){
  if(nrow(cv_entries_tibble) > 9){
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 2, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  } else {
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  }
}

# function for making a year blank when it's the same as the one preceding it
blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year = as.character(year),
           year = case_when(
             row_number == 1 ~ year,
             year == lag(year) ~ "",
             year != lag(year) ~ year
           ))
}

####### READ IN DATA
#### publications #####
publications <- read_csv("_content/publications.csv") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  mutate(authors_full = str_replace(authors_full, "E\\. Hurwitz", "**E\\. Hurwitz**")) %>%
  mutate(authors_full = str_replace(authors_full, "E\\. S\\. Hurwitz", "**E\\. S\\. Hurwitz**")) %>%   
  # make my name bold
  mutate(year = year(date)) %>% 
  mutate(venue_abbrev = if_else(!is.na(venue_abbrev), str_c(venue_abbrev, ": "), "")) # make the abbrevation an empty string if NA; add a colon and a space after if it if there is one

#Add months to dates
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year = year(date),
         month = months(date),
         month = str_sub(month, 1, 3)) %>%
  mutate(year_end = case_when(
    date_end == "Present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  ),
  month_end = case_when(
    date_end == "Present" ~ "",
    !is.na(date_end) ~ str_sub(months(as_date(date_end)), 1, 3),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(dateFormatted = ifelse((is.na(year_end) | is.na(month_end) | (year == year_end & month == month_end)),
                                str_c(month, " ", year),
                                str_c(month, " ", year, " ---<br>", month_end, " ", year_end)))

```

<!-- ::: {.title} -->
<h1 class="title2">Ethan Hurwitz</h1>
<!-- ::: -->

<div class="subtitle">University of California, San Diego<br>
Department of Psychology</div><br>

<table class="contacts">
    <tr class="contacts2">
        <td><i class="fa fa-envelope"></i> ehurwitz\@ucsd.edu</td>
        <td><i class="fas fa-globe"></i> www.EthanHurwitz.com</td>
        <td><i class="fab fa-github"></i> EthanHurwitz</td>
        <!-- <td><i class="ai ai-osf"></i> OSF: phyeb</td> -->
        <!-- <td><a href="https://scholar.google.com/citations?user=hciXZQQAAAAJ"><i class="ai ai-google-scholar ai-lg"></i> Scholar</a></td> -->

    </tr>
</table> 


<div class="cv-entries">

## Education

```{r education}
cv_entries %>% 
  filter(type == 'education' & is.na(exclude)) %>%
  mutate(what = glue("<span class='cv-entry-title'><b>{what}</b></span>, {where}<br>", 
                      "{additional_info}<br>",
                      "<span class='thesis-title'>{additional_info2}</span>")) %>%
  mutate(what = gsub("NA", "", what)) %>%
  mutate(what = gsub("<br><br>", "<br>", what)) %>%
  #select(year, what) %>% 
  select(dateFormatted, what) %>%
  kable()
```

## Grants and Funding

```{r grants}
cv_entries %>%
  filter(type == 'major_grants' & is.na(exclude)) %>%
  mutate(what = if_else(is.na(additional_info),
                        glue("<span class='cv-entry-title'><b>{what}</b></span> ({additional_info2}), {where}"),
                        glue("<span class='cv-entry-title'><b>{what}</b></span> ({additional_info2}), {where}.<br>{additional_info}"))) %>%
  select(year, what) %>%
  kable()
```

## Awards and Honors

```{r awards}
cv_entries %>% 
  filter(type == 'awards' & is.na(exclude)) %>% 
  mutate(what = ifelse(is.na(where), glue("<span class='cv-entry-title'>{what}</span>"), glue("<span class='cv-entry-title'>{what}</span>, {where}"))) %>%  
  blank_year_when_repeated() %>% 
  select(year, what) %>% 
  kable()
```


## Publications
<!-- :::::: {.grid-container-publications} -->
### Peer-Reviewed Journal Articles

```{r journal publications}
publications %>%
  filter(type == "journal article" & is.na(exclude)) %>% 
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}, {volume}</span>",
                         ", <span class='publication-venue'>{pages}. </span>",
                         "<span class='publication-doi'>{doi}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()
```

### Peer-Reviewed Conference Publications

```{r conference publications}
publications %>%
  filter(type == "conference paper" & is.na(exclude)) %>%
    # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honorable") ~ glue("<br><i class='fas fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}</span>",
                         ", <span class='publication-venue'>{pages}. </span>",
                         "<span class='conference-venue'>{venue}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()

```

<!-- <br class="pageBreak"> -->

<!--
<h3>Book chapters</h3>

```{r}
publications %>% 
  filter(type == "book chapter") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}: {venue}</span>")) %>%
  padding_function(., "B") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()

```

<h3>Extended abstracts and workshop papers <br><span class="review-note"></span></h3>

```{r}
publications %>%
  filter(type == "extended abstract" | type == "workshop paper") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev} {venue}</span>")) %>%
  padding_function(., "A") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()

```
-->

## Conference Presentations

### Oral Presentations

```{r conference talks}
publications %>% 
  filter(type == 'conference talk' & is.na(exclude)) %>%
    # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honorable") ~ glue("<br><i class='fas fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}</span>",
                         ", <span class='conference-venue'>{venue}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()

```

### Poster Presentations
<!--Decide how to organize this in the googlesheet and clean it up.-->
```{r poster presentations}
publications %>% 
  filter(type == 'poster' & is.na(exclude)) %>%
    # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honorable") ~ glue("<br><i class='fas fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}</span>",
                         ", <span class='conference-venue'>{venue}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()

```

## Invited Talks 

```{r invited talks}
cv_entries %>% 
  filter(type == 'talk' & subtype == "invited" & is.na(exclude)) %>%
  # create citations
  mutate(citation = glue("<span class='publication-venue'>{where} {institution} -- </span>",
                         "<span class='cv-entry-title' style='font-style: italic;'>{what} </span>({dateFormatted})")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()

```

## Teaching Experience

### Instructor of Record

```{r instructor}
cv_entries %>% 
  filter(type == 'teaching' & subtype == "instructor" & is.na(exclude)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "<span class='items' style='padding-left: 20px'>{where} </span>"),
         year = ifelse(is.na(year), glue(""), year)) %>%
  select(year, what) %>% 
  kable()
```

### Teaching Assistanceships

```{r TA}
cv_entries %>% 
  filter(type == 'teaching' & subtype == "TA" & is.na(exclude)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "<span class='items' style='padding-left: 20px'>{where} </span>"),
         year = ifelse(is.na(year), glue(""), year)) %>%
  select(year, what) %>% 
  kable()
```

### Senior TA

```{r SeniorTA}
cv_entries %>% 
  filter(type == 'work' & subtype == "seniorTA") %>% 
    mutate(what = glue("<span class='cv-entry-title'>{institution}</span><br>",
           "{department}<br>", "<b>{where}</b><br>",
           "<br>-- ", "{cv_entries %>% 
    filter(type == 'work' & subtype == 'seniorTA') %>%
    pull(additional_info) %>% gsub(';', '<br>-- ', .)}")) %>%
  select(dateFormatted, what) %>% 
  kable()
```

## Service, Outreach, and Professional Activities

### Reviewer:

```{r reviewer}
cv_entries %>% 
  filter(type == 'professional-activities' & subtype == "reviewer" & is.na(exclude)) %>% 
  mutate(where = glue("<span class='cv-entry-title'>{where}</span>"),
         year = ifelse(is.na(year), glue(""), year)) %>%
  select(year, where) %>% 
  kable()
```


<!-- ```{r} -->
<!-- cv_entries %>%  -->
<!--   filter(type == 'service') %>%  -->
<!--   mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) %>%  -->
<!--   mutate(what = glue("<span class='cv-entry-title'>{what}</span> {where}")) %>% -->
<!--   arrange(desc(date_end), desc(date)) %>%  -->
<!--   select(year, what) %>%  -->
<!--   kable() -->
<!-- ``` -->

<!-- <br class="pageBreak"> -->

## Clinical Experience

### Research Program Coordinator

```{r clinical experience}
cv_entries %>% 
  filter(type == 'work' & subtype == "Hopkins") %>% 
    mutate(what = glue("<span class='cv-entry-title'>{institution}</span><br>",
           "{department}<br>", "{cv_entries %>% 
    filter(type == 'work' & subtype == 'Hopkins') %>%
    pull(where) %>% gsub(';', '<br>', .)}", "<br>",
           "<br>-- ", "{cv_entries %>% 
    filter(type == 'work' & subtype == 'Hopkins') %>%
    pull(additional_info) %>% gsub(';', '<br>-- ', .)}")) %>%
  select(dateFormatted, what) %>% 
  kable()
```

<!-- close 'cv-entries' div -->
</div>


<!-- Below is a list of other code that could be used to generate different CV items. It may be useful to those who are more professionally developed than I -->

<!-- ## Publicly available research code & data -->

<!-- ```{r} -->
<!-- pubs_w_number <- publications %>%  -->
<!--   select(type, authors_full, date, title, materials) %>%  -->
<!--   mutate(inclusive_type = if_else(type == "workshop paper" | type == "extended abstract", "abstract", type)) %>%  -->
<!--   group_by(inclusive_type) %>%  -->
<!--   arrange(date) %>%  -->
<!--   mutate(number = row_number())#, -->
<!--          #number = case_when( -->
<!--            #inclusive_type == "conference paper" ~ glue("[C{number}]"), -->
<!--            #inclusive_type == "journal article" ~ glue("[J{number}]"), -->
<!--            #inclusive_type == "abstract" ~ glue("[A{number}]"), -->
<!--         #   TRUE ~ "" -->
<!--         # )) -->

<!-- public_code <- cv_entries %>%  -->
<!--   filter(type == 'open_research' & is.na(exclude)) %>%  -->
<!--   select(what, additional_info) %>%  -->
<!--   rename(title = additional_info) %>%  -->
<!--   left_join(pubs_w_number) -->

<!-- public_code %>%  -->
<!--   mutate(year = year(date)) %>%  -->
<!--   mutate(what = glue("<span class='cv-entry-title'>{what} {number}</span><br>",  -->
<!--                       "{authors_full}<br>", -->
<!--                       "{materials}")) %>%  -->
<!--   arrange(desc(date)) %>%  -->
<!--   select(year, what) %>%  -->
<!--   blank_year_when_repeated() %>%  -->
<!--   kable() -->
<!-- ``` -->



<!--- ### Podcasts {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'talk-podcast') %>% 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) %>% 
  replace_na(list(what_translation = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what} <span class='cv-entry-translation'>{what_translation}</span>")) %>%
  padding_function(., "Pod") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()

```

```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year, what) %>% 
  kable()
```

<!-- 
### Discussion panels {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'talk-panel') %>%
  mutate(additional_info = if_else(is.na(additional_info), "", additional_info)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what},  {additional_info}")) %>%
  padding_function(., "D") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()

```

### Blog posts {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'pop-writing') %>%
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what}")) %>%
  padding_function(., "B") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()
```
--->

<!-- <br class="pageBreak"> -->

<!--
## Professional development
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  select(year, what) %>% 
  kable()
```
-->
<!-- 
## Minor grants and funding
```{r}
cv_entries %>%
  filter(type == 'minor_grants') %>%
  mutate(what = if_else(!is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br> ", 
                             "{additional_info}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"))) %>%
  blank_year_when_repeated() %>% 
  select(year, what) %>%
  kable()
```
-->
<!-- <br class="pageBreak"> -->

<!-- 
## Volunteering {.packages}

```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  mutate(what = if_else(!is.na(additional_info), glue("{what}<br>{additional_info}"), what)) %>%
  arrange(desc(date), desc(date_end)) %>% 
  select(year, what) %>%
  kable()
```
-->
<!-- <br class="pageBreak"> -->



<!-- Include the line below if you want links to be included as a footnote.-->
<!-- # Links -->

