---
output:
  pagedown::html_paged:
    css: ["css/one-column-paged-academic.css", "css/academicons.min.css",
          "css/css/all.css"]
#"https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: false
title: "Ethan Hurwitz CV"
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
library(glue)
library(googlesheets4)

######## rerun googlesheet syncing to make sure files are up to date!
source("sync_w_gsheets.R", local = knitr::knit_global())

######## CREATE HELPER FUNCTIONS
# function which takes a name and replaces the first name with initial and dot
replace_first_name_with_initial_and_dot <- function(author_name) {
  str_replace(author_name, "(?<=\\S)\\S+", "\\.")
}

# function for doing this for an entry with a number of authors
replace_first_names_in_list_with_initial_and_dot <- function(authors){
  authors_split <- str_split(authors, ",") %>% 
    map(str_trim)
  
  authors_split[[1]] %>% map_chr(replace_first_name_with_initial_and_dot) %>% 
    paste0(collapse = ", ")
}

# function for adding leading zero's when there's more than 10 entries
padding_function <- function(cv_entries_tibble, letter_to_pad){
  if(nrow(cv_entries_tibble) > 9){
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 2, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  } else {
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  }
}

# function for making a year blank when it's the same as the one preceding it
blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year = as.character(year),
           year = case_when(
             row_number == 1 ~ year,
             year == lag(year) ~ "",
             year != lag(year) ~ year
           ))
}

####### READ IN DATA
#### publications #####
publications <- read_csv("_content/publications.csv") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  mutate(authors_full = str_replace(authors_full, "E\\. Hurwitz", "**E\\. Hurwitz**")) %>%
  mutate(authors_full = str_replace(authors_full, "E\\. S\\. Hurwitz", "**E\\. S\\. Hurwitz**")) %>%   
  # make my name bold
  mutate(year = year(date)) %>% 
  mutate(venue_abbrev = if_else(!is.na(venue_abbrev), str_c(venue_abbrev, ": "), "")) # make the abbrevation an empty string if NA; add a colon and a space after if it if there is one

#Add months to dates
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year = year(date),
         month = months(date),
         month = str_sub(month, 1, 3)) %>%
  mutate(year_end = case_when(
    date_end == "Present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  ),
  month_end = case_when(
    date_end == "Present" ~ "",
    !is.na(date_end) ~ str_sub(months(as_date(date_end)), 1, 3),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(dateFormatted = ifelse((is.na(year_end) | is.na(month_end) | (year == year_end & month == month_end)),
                                str_c(month, " ", year),
                                str_c(month, " ", year, " ---<br>", month_end, " ", year_end)))

```

```{r header, comments=NA}
source(here::here("source.R"))

# data.frame("temp" = c(glue('<div class="cv-entries">','<h1 class="title2">{fullName}</h1>','</div>'),
#                       glue('<div class="subtitle">', institution, '</div><br>'),
#                       glue('<table class="contacts">
#     <tr class="contacts2">',
#     ifelse(Email.show,
#            glue('<td><i class="fa fa-envelope"></i>', Email, '</td>'), ""),
#     ifelse(Website.show,
#            glue('<td><i class="fas fa-globe"></i>',Website,'</td>'), ""),
#     ifelse(Github.show,
#            glue('<td><i class="fab fa-github"></i>',Github,'</td>'), ""),
#     ifelse(OSF.show,
#            glue('<td><i class="ai ai-osf"></i> OSF: ', OSF, '</td>'), ""),
#     ifelse(Scholar.show,
#            glue('<td><a href="', Scholar, '"><i class="ai ai-google-scholar ai-lg"></i> Scholar</a></td>'), ""),
#     '</tr>
# </table> '))) %>%
#   kable(col.names = NULL)

#glue('<div class="cv-entries">','<h1 class="title2">{fullName}</h1>','</div>') #%>%

# glue('<div class="subtitle">', institution, '</div><br>')
# 
# glue('<table class="contacts">
#     <tr class="contacts2">',
    # ifelse(Email.show,
    #        glue('<td><i class="fa fa-envelope"></i>', Email, '</td>'), ""),
    # ifelse(Website.show,
    #        glue('<td><i class="fas fa-globe"></i>',Website,'</td>'), ""),
    # ifelse(Github.show,
    #        glue('<td><i class="fab fa-github"></i>',Github,'</td>'), ""),
    # ifelse(OSF.show,
    #        glue('<td><i class="ai ai-osf"></i> OSF: ', OSF, '</td>'), ""),
    # ifelse(Scholar.show,
    #        glue('<td><a href="', Scholar, '"><i class="ai ai-google-scholar ai-lg"></i> Scholar</a></td>'), ""),
#     '</tr>
# </table> ')
```

<h1 class="title2">`r fullName`</h1>

<div class="subtitle">`r institution`</div><br>

<table class="contacts">
    <tr class="contacts2">
        `r glue(
            ifelse(Email.show,
           glue('<td><i class="fa fa-envelope"></i>', Email, '</td>'), ""),
    ifelse(Website.show,
           glue('<td><i class="fas fa-globe"></i>',Website,'</td>'), ""),
    ifelse(Github.show,
           glue('<td><i class="fab fa-github"></i>',Github,'</td>'), ""),
    ifelse(OSF.show,
           glue('<td><i class="ai ai-osf"></i>', OSF, '</td>'), ""),
    ifelse(Scholar.show,
           glue('<td><a href="', Scholar, '"><i class="ai ai-google-scholar ai-lg"></i> Scholar</a></td>'), "")
        )`
    </tr>
</table>

<div class="cv-entries">

<!--Below, each CV section is segemented into it's own chunk. The relevant code is sandwiched between comments denoting where the respective code for that section begins and ends. If you want to change the order in which these appear in your CV, simply cut/paste the entire section (including the comments for the section's beginning and end) and place them in the order you prefer!-->

<!-- Section for Education begin -->
`r ifelse(Education.show, glue("## Education"))`

`r if(Education.show){cv_entries %>%
  filter(type == 'education' & is.na(exclude)) %>%
  mutate(what = glue("<span class='cv-entry-title'><b>{what}</b></span>, {where}<br>",
                     "{additional_info}<br>",
                     "<span class='thesis-title'>{additional_info2}</span>")) %>%
  mutate(what = gsub("NA", "", what)) %>%
  mutate(what = gsub("<br><br>", "<br>", what)) %>%
  #select(year, what) %>%
  select(dateFormatted, what) %>%
  kable()}`
<!-- Section for Education begin -->

<!-- Section for Grants and Funding begin -->
`r ifelse(GrantsFunding.show, glue("## Grants and Funding"))`

`r if(GrantsFunding.show){cv_entries %>%
  filter(type == 'major_grants' & is.na(exclude)) %>%
  mutate(what = if_else(is.na(additional_info),
                        glue("<span class='cv-entry-title'><b>{what}</b></span> ({additional_info2}), {where}"),
                        glue("<span class='cv-entry-title'><b>{what}</b></span> ({additional_info2}), {where}.<br>{additional_info}"))) %>%
  select(year, what) %>%
  kable()}`
<!-- Section for Grants and Funding end -->

<!-- Section for Awards and Honors begin -->
`r ifelse(AwardsHonors.show, glue("## Awards and Honors"))`

`r if(AwardsHonors.show){cv_entries %>% 
  filter(type == 'awards' & is.na(exclude)) %>% 
  mutate(what = ifelse(is.na(where), glue("<span class='cv-entry-title'>{what}</span>"), glue("<span class='cv-entry-title'>{what}</span>, {where}"))) %>%  
  blank_year_when_repeated() %>% 
  select(year, what) %>% 
  kable()}`
<!-- Section for Awards and Honors end -->

<!-- Section for Publications begin -->
`r ifelse(Publications.show, glue("## Publications"))`

`r ifelse(Journals.pub.show, glue("### Peer-Reviewed Journal Articles"))`
`r if(Journals.pub.show){publications %>%
  filter(type == "journal article" & is.na(exclude)) %>% 
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}, {volume}</span>",
                         ", <span class='publication-venue'>{pages}. </span>",
                         "<span class='publication-doi'>{doi}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()}`

`r ifelse(Proceedings.pub.show, glue("### Peer-Reviewed Conference Publications"))`
`r if(Proceedings.pub.show){publications %>%
  filter(type == "conference paper" & is.na(exclude)) %>%
    # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honorable") ~ glue("<br><i class='fas fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}</span>",
                         ", <span class='publication-venue'>{pages}. </span>",
                         "<span class='conference-venue'>{venue}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()}`

<!-- <br class="pageBreak"> -->

<!--
<h3>Book chapters</h3>

```{r}
publications %>% 
  filter(type == "book chapter") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}: {venue}</span>")) %>%
  padding_function(., "B") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()

```

<h3>Extended abstracts and workshop papers <br><span class="review-note"></span></h3>

```{r}
publications %>%
  filter(type == "extended abstract" | type == "workshop paper") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev} {venue}</span>")) %>%
  padding_function(., "A") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()

```
-->

<!-- Section for Publications end -->


<!-- Section for Conference Presentations begin -->
`r ifelse(Conference.show, glue("## Conference Presentations"))`

`r ifelse(Conference.oral.show, glue("### Oral Presentations"))`
`r if(Conference.oral.show){publications %>% 
  filter(type == 'conference talk' & is.na(exclude)) %>%
    # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honorable") ~ glue("<br><i class='fas fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}</span>",
                         ", <span class='conference-venue'>{venue}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()}`

`r ifelse(Conference.poster.show, glue("### Poster Presentations"))`
`r if(Conference.poster.show){publications %>% 
  filter(type == 'poster' & is.na(exclude)) %>%
    # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honorable") ~ glue("<br><i class='fas fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='publication-authors'>{authors_full} ({year}).</span> ",
                         "<span class='cv-entry-title'>{title}. </span>",
                         "<span class='publication-venue' style='font-style: italic;'>{publication}</span>",
                         ", <span class='conference-venue'>{venue}. </span>")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()}`
<!--Decide how to organize this in the googlesheet and clean it up.-->

<!-- Section for Conference Presentations end -->

<!-- Section for Invited Talks begin -->
`r ifelse(Talks.show, glue("## Invited Talks "))`
`r if(Talks.show){cv_entries %>% 
  filter(type == 'talk' & subtype == "invited" & is.na(exclude)) %>%
  # create citations
  mutate(citation = glue("<span class='publication-venue'>{where} {institution} -- </span>",
                         "<span class='cv-entry-title' style='font-style: italic;'>{what} </span>({dateFormatted})")) %>%
  mutate(citation = gsub("NA", "", citation)) %>%
  mutate(citation = gsub(", . ht", ".", citation)) %>% #fix this.
  padding_function(., "") %>% 
  blank_year_when_repeated() %>%
  #select(year, number, citation) %>%
  select(year, citation) %>%
  knitr::kable()}`

<!-- Section for Invited Talks end -->

<!-- Section for Teaching Experience begin -->
`r ifelse(Teaching.show, glue("## Teaching Experience"))`

`r ifelse(Teaching.instructor.show, glue("### Instructor of Record"))`
`r if(Teaching.instructor.show){cv_entries %>% 
  filter(type == 'teaching' & subtype == "instructor" & is.na(exclude)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "<span class='items' style='padding-left: 20px'>{where} </span>"),
         year = ifelse(is.na(year), glue(""), year)) %>%
  select(year, what) %>% 
  kable()}`

`r ifelse(Teaching.TA.show, glue("### Teaching Assistanceships"))`
`r if(Teaching.TA.show){cv_entries %>% 
  filter(type == 'teaching' & subtype == "TA" & is.na(exclude)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "<span class='items' style='padding-left: 20px'>{where} </span>"),
         year = ifelse(is.na(year), glue(""), year)) %>%
  select(year, what) %>% 
  kable()}`

`r ifelse(Teaching.seniorTA.show, glue("### Senior TA"))`
`r if(Teaching.seniorTA.show){cv_entries %>% 
  filter(type == 'work' & subtype == "seniorTA") %>% 
    mutate(what = glue("<span class='cv-entry-title'>{institution}</span><br>",
           "{department}<br><br>", "<b>{where}</b>",
           "<br>-- ", "{cv_entries %>% 
    filter(type == 'work' & subtype == 'seniorTA') %>%
    pull(additional_info) %>% gsub(';', '<br>-- ', .)}")) %>%
  select(dateFormatted, what) %>% 
  kable()}`
<!-- Section for Teaching Experience end -->

<!-- Section for Service, Outreach, and Professional Activities begin -->
`r ifelse(SOP.show, glue("## Service, Outreach, and Professional Activities"))`

`r ifelse(SOP.reviewer.show, glue("### Reviewer"))`
`r if(SOP.reviewer.show){cv_entries %>% 
  filter(type == 'professional-activities' & subtype == "reviewer" & is.na(exclude)) %>% 
  mutate(where = glue("<span class='cv-entry-title'>{where}</span>"),
         year = ifelse(is.na(year), glue(""), year)) %>%
  select(year, where) %>% 
  kable()}`

<!-- ```{r} -->
<!-- cv_entries %>%  -->
<!--   filter(type == 'service') %>%  -->
<!--   mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) %>%  -->
<!--   mutate(what = glue("<span class='cv-entry-title'>{what}</span> {where}")) %>% -->
<!--   arrange(desc(date_end), desc(date)) %>%  -->
<!--   select(year, what) %>%  -->
<!--   kable() -->
<!-- ``` -->

<!-- <br class="pageBreak"> -->

<!-- Section for Service, Outreach, and Professional Activities end -->

<!-- Section for Clinical Experience begin -->

`r ifelse(ClinicalExp.show, glue("## Clinical Experience"))`

`r ifelse(ClinicalExp.RPC.show, glue("### Research Program Coordinator"))`

`r if(ClinicalExp.RPC.show){cv_entries %>% 
  filter(type == 'work' & subtype == "Hopkins") %>% 
    mutate(what = glue("<span class='cv-entry-title'>{institution}</span><br>",
           "{department}<br>", "{cv_entries %>% 
    filter(type == 'work' & subtype == 'Hopkins') %>%
    pull(where) %>% gsub(';', '<br>', .)}", "<br>",
           "<br>-- ", "{cv_entries %>% 
    filter(type == 'work' & subtype == 'Hopkins') %>%
    pull(additional_info) %>% gsub(';', '<br>-- ', .)}")) %>%
  select(dateFormatted, what) %>% 
  kable()}`

<!-- Section for Clinical Experience end -->


<!-- close 'cv-entries' div -->
</div>


<!-- Below is a list of other code that could be used to generate different CV items. It may be useful to those who are more professionally developed than I -->

<!-- ## Publicly available research code & data -->

<!-- ```{r} -->
<!-- pubs_w_number <- publications %>%  -->
<!--   select(type, authors_full, date, title, materials) %>%  -->
<!--   mutate(inclusive_type = if_else(type == "workshop paper" | type == "extended abstract", "abstract", type)) %>%  -->
<!--   group_by(inclusive_type) %>%  -->
<!--   arrange(date) %>%  -->
<!--   mutate(number = row_number())#, -->
<!--          #number = case_when( -->
<!--            #inclusive_type == "conference paper" ~ glue("[C{number}]"), -->
<!--            #inclusive_type == "journal article" ~ glue("[J{number}]"), -->
<!--            #inclusive_type == "abstract" ~ glue("[A{number}]"), -->
<!--         #   TRUE ~ "" -->
<!--         # )) -->

<!-- public_code <- cv_entries %>%  -->
<!--   filter(type == 'open_research' & is.na(exclude)) %>%  -->
<!--   select(what, additional_info) %>%  -->
<!--   rename(title = additional_info) %>%  -->
<!--   left_join(pubs_w_number) -->

<!-- public_code %>%  -->
<!--   mutate(year = year(date)) %>%  -->
<!--   mutate(what = glue("<span class='cv-entry-title'>{what} {number}</span><br>",  -->
<!--                       "{authors_full}<br>", -->
<!--                       "{materials}")) %>%  -->
<!--   arrange(desc(date)) %>%  -->
<!--   select(year, what) %>%  -->
<!--   blank_year_when_repeated() %>%  -->
<!--   kable() -->
<!-- ``` -->



<!--- ### Podcasts {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'talk-podcast') %>% 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) %>% 
  replace_na(list(what_translation = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what} <span class='cv-entry-translation'>{what_translation}</span>")) %>%
  padding_function(., "Pod") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()

```

```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year, what) %>% 
  kable()
```

<!-- 
### Discussion panels {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'talk-panel') %>%
  mutate(additional_info = if_else(is.na(additional_info), "", additional_info)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what},  {additional_info}")) %>%
  padding_function(., "D") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()

```

### Blog posts {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'pop-writing') %>%
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what}")) %>%
  padding_function(., "B") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()
```
--->

<!-- <br class="pageBreak"> -->

<!--
## Professional development
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  select(year, what) %>% 
  kable()
```
-->
<!-- 
## Minor grants and funding
```{r}
cv_entries %>%
  filter(type == 'minor_grants') %>%
  mutate(what = if_else(!is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br> ", 
                             "{additional_info}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"))) %>%
  blank_year_when_repeated() %>% 
  select(year, what) %>%
  kable()
```
-->
<!-- <br class="pageBreak"> -->

<!-- 
## Volunteering {.packages}

```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  mutate(what = if_else(!is.na(additional_info), glue("{what}<br>{additional_info}"), what)) %>%
  arrange(desc(date), desc(date_end)) %>% 
  select(year, what) %>%
  kable()
```
-->
<!-- <br class="pageBreak"> -->



<!-- Include the line below if you want links to be included as a footnote.-->
<!-- # Links -->

